Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
wip

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{figs/cyclic}
	\caption{
		\OPT  collocates 5 pairs, paying one migration per pair.
	Dashed lines represent requests.
	An arrow, e.g.~from $b_1$ to $a_1$ means  that $b_1$ replaces $a_1$. }
	\label{fig:cyclic}
\end{figure}

@@

\noindent
\textbf{The charging scheme.}
We charge both \OPT and \RM whenever \RM collocates a~pair.%(i.e., on a~collocation event).
\RM collocates a~pair always with a~swap,%(i.e., two simultaneous migrations),
which  costs $2\alpha$,
while \OPT may save some costs by collocating multiple pairs at once.
% before they inflict too much communication cost.
 Therefore it pays the price of only one migration per pair  (see Figure \ref{fig:cyclic}).
Hence,
whenever \OPT collocates a~pair,
we charge it only the cost of moving a~single node to the cluster of the other,
i.e., $\alpha$ (in contrast to $2\alpha$ on \RM).

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.4\textwidth]{figs/cyclic}
	\caption{
		\OPT  collocates 5 pairs, paying one migration per pair.
	Dashed lines represent requests.
	An arrow, e.g.~from $b_1$ to $a_1$ means  that $b_1$ replaces $a_1$.\maciek{Maybe: "An arrow from $a$ to $b$ means that $b$ replaces $a$.". Or "$b$ migrates in place of $a$."} }
	\label{fig:cyclic}
\end{figure}

@@

\noindent
\textbf{The charging scheme.}
We charge both \OPT and \RM whenever \RM collocates a~pair.%(i.e., on a~collocation event).
\RM collocates a~pair always with a~swap,%(i.e., two simultaneous migrations),
which  costs $2\alpha$,
while \OPT may save some costs by collocating multiple pairs at once.
% before they inflict too much communication cost.
 Thus it pays the price of only one migration per pair  (see Figure \ref{fig:cyclic}).
Whenever \OPT collocates a~pair,
we charge it only the cost $\alpha$ of moving a~single node to the other cluster (in contrast to the cost $2\alpha$ incurred by \RM).
